\documentclass[main.tex]{subfiles}
\begin{document}
	
	\chapter{Distribution of Tasks}
		\chapterauthor{Merete Bommarius}
		\section{Planning:}
		The task that Planning is focusing on that the moment is the integration of the interfaces and communication from and between the different groups. The group is also responsible for the errorhandling, which means that they act as a middle-man between groups in order to gain access to all sides, which makes it easier to identify and correct possible errors.
		
		\section{Perception:}
		The goal for the Perception group is to perceive, and identify objects in a given location, which in our case is a table. They also have to differenciate between objects if it the same one with just slight differences, for example the color. After Perception identifies the object, they  will extract the information and forward it for further processing. For this, they are triggered by planning and communicate furthermore with Knowledge.
		
		\section{Manipulation:}
		Manipulation‘s job was it to create actionservers to incorporate the different physical actions that the HSR can take; grabbing, putting down, and knocking over varies objects. Every one of those action have to be doable with the gripper attached to the robot.Navigation:Navigation works closely together with Manipulaton. While Manipulation works on the physical actions that can be performed with the gripper, Navigation focuses on the HSR‘s movements. Here, they pay special attention to the robot‘s surroundings and make sure there is an anti-collision server in place to aviod collision with any objects.
		
		\section{Knowledge:}
		The task Knowledge had was to establish a knowledge base, where the other group could save information into. This knowledge base is supposed to contain the dimensions,color, and weight of an object but it is also supposed to use the visual data gathered from Perception to identify and categorize the object.There was, however, a problem with the knowledge base which was not managed to get fixed in time to get tested, so Knowledge will not be showcased in the demonstration that will be held on 12-20-2019.
		
		\section{NLP:}
		Albeit this part of the project has not been included in the robot yet, there has been progress. The HSR is supposed to talk back, when you interact with it. Right now NLP is working on training the parsers so that the robot is able to understand what exactly it is that you want it to do. 
\end{document}