\documentclass[main.tex]{subfiles}
\begin{document}
	
	\chapter{Distribution of Tasks}
		\chapterauthor{Merete Bommarius}

		\section{Planning:}
		The task that Planning is focusing on that the moment is the integration of the interfaces and communication from and between the different groups. The group is also responsible for the errorhandling, which means that they act as a middle-man between groups in order to gain access to all sides, which makes it easier to identify and correct possible errors.
		
		\section{Perception:}
		Perception is responsible for perceiving and interpreting images of the world. This includes performing various operations on the camera data to enhance performance, as well as detecting and classifying objects. Perception also provides training data to use for object classification.
		
		
		\section{Manipulation:}
		Manipulation is responsible for interacting with the real world. This means the collision free grasping and placing of objects. Another side task is to have the HSR take certain poses for better observation of the world. 
		
		\section{Knowledge:}
		The Knowledgebase has been implemented rather early on in this Milestone, it being one of the highest priorities. We still need to implement a few things but those are minor, and the Knowledge part of the SUTURO project will be able to be showcased in the second Milestone. 
		
		\section{NLP:}
		Albeit this part of the project has not been fully included in the robot yet, there has been progress. There are commands which start and stop the current task the robot is doing, being "Robot start" and "Robot stop". Currently there are still some changes that need to be made to make this feature fully functional. NLP is also focusing on readying the output that the HSR is supposed to give in certain situations. An Elaboration on this topic follows later in the NLP section of the documentation.  
		
		\section{Navigation}
		Navigation takes care of driving the robot from one position to another while avoiding any obstacles on the way. In this Milestone an additional task has been added. The detection of obstacles which have not been mapped and therefore may be an point of interest.
\end{document}
