\documentclass[main.tex]{subfiles}
\begin{document}
	
	\chapter{Challenges}
		\chapterauthor{Evan Kapitzke}

	\section{General}
	The codefreeze that was supposed to start two weeks before the final milestone presentation got interrupted by
	problems in Perception and Knowledge. 	

	\section{Planning}
	First of all, in this milestone Planning had to integrate Knowledge. The creation of high level plans was the second main goal,
	in order to allow error handling.
	The final integration phase was really stressful, because there was not much time left to test the final results.

	\section{Perception}
	We had to solve some problems regarding the region filter.
	Additionally, the action server stopped working two weeks before the second milestone presentation.
	Solving this issue was a high priority in order to let the other groups test their work.	

	\section{Manipulation}
	Manipulation needs to be able to grasp objects from different angels.
	For this purpose additional functions got implemented.
	
	\section{Knowledge}
	There were some issues regarding the object class labels. Everything got classified as "banana".
	This issue got solved but for short period of time Planning was unable to insert objects into
	the knowledge-base.

	\section{NLP}
	NLP had to find a way to connect the Python2.7 and Python3 interfaces.
	The solution was "tinyrpc".

	\section{Navigation}
	Some areas in the lab hinder the movement of the HSR. Navigation solved this issue by creating
	an additional node, which translates navigation goals from Planning into smaller-stepped navigation goals.
	This node solved the movement issue in the lab.

	\newpage
		
\end{document}
