\documentclass[main.tex]{subfiles}
\begin{document}
	\chapter{Organization}
	\chapterauthor{Marc Stelter}
	
	\section{Schedule}
	The project ran from the 13.10.2019 to 31.05.2020. During this time window the following dates have been set:
	\begin{itemize}
		\item 20.12.2019 Milestone 1: Get used to the new technologies and develop a minimal running setup.
		\item 06.03.2020 Milestone 2: Finish a working setup for the tasks grocery storing and clean up
		\item Early April 2020: Project day Uni Bremen
		\item End of April 2020: RoboCup German Open
		\item 08.05.2020: Third Milestone: End of Development
		\item 31.05.2020: Due date Project documentation
	\end{itemize}

	\section{Structure}
	Going by the different challenges of the project and the suggestions of the tutors subgroups have been formed. Each specializing in a certain aspect of the project. 
	The groups are as follow:
	\begin{itemize}
		\item Navigation: localization and navigation.
		\item Perception: recognizing and categorizing objects.
		\item Manipulation: interacting with the world.
		\item Knowledge: save and associate gained information.
		\item NLP: speech recognition.
		\item Planning: decision making of the HSR.
	\end{itemize}   

	\section{Procedure model}
	The procedure model is a custom scrum variation. Instead of the fixed sprint length we decided to adjust the length of each sprint as needed. Additionally the daily stand ups have been omitted, since the project only has a 16 hour per week workload.
	
	Each Friday a plenum with the tutors was held where we presented the current progress, discussed further strategies and clarified organizational matters.
	
	In addition an internal meeting was be held each Friday discussing the internal organization and integrating the progress of the different sub groups.
	
	\textit{TODO: Create diagram of procedure model and add here}

	\section{Roles}
	The roles have been assigned for each milestone, while making sure each person holds at least two roles over the course of the project. The roles have been assigned as follows:
	\begin{itemize}
		\item Scrum master / Project leader: organizing plenum and sprints. Push decision making.
		\item Product owner: take care of backlog
		\item Kanban master: takes care of the kanban board
		\item Foreign minister: external representation and organization of project day
		\item Group leader: organization of sub groups
		\item Quality assessment: check documents and code for errors.
	\end{itemize}

	The foreign minister is excepted from changes on each milestone.
	
	\section{Software}
	The following applications or services have been used in the organization of the project:
	\begin{itemize}
		\item Microsoft teams: Chat interaction, wiki, protocols, presentations.
		\item Trello: Kanban board
		\item Github: Repository for the project code
	\end{itemize}  

	\section{Corona}
	Due to the outbreak of the Corona virus and the following regulations access to the HSR was no longer possible as of 16.03.2020. Therefore the following development has been done with the gazebo simulator.
	The meetings have been carried out via Jitsi and Discord. An additional project computer has been provided to run the simulation.
	The project day and RoboCup have been canceled.
	
\end{document}